Trajipaq_sentiment_cr

### 2023-08-10 1. Trajipaq_sentiment/2. Codes/Trajipaq_sentiment_cr.Rmd
update WGI

trajipaq <- merge(trajipaq, wgidataset, by.x = c("annee_qc", "Q11"),
                by.y = c("year", "countryname"), all.x = TRUE)

wgidataset_2021 <- filter(wgidataset, year == 2021)
wgidataset_canada <- filter(wgidataset, countryname == "Canada")

trajipaq <- trajipaq %>%
  left_join(wgidataset_2021, by = c("Q11" = "countryname"))%>%
  left_join(wgidataset_canada, by = c("annee_qc" = "year"))

trajipaq <- trajipaq %>%
  rename_with(~sub("\\.y$", "_2021", .), ends_with(".y"))%>%
  rename_with(~sub("\\.x$", "_arrival", .), ends_with(".x"))

>>>>

trajipaq <- merge(trajipaq, wgidataset, by.x = c("annee_qc", "Q11"), # Origine à l'arrivée
                by.y = c("year", "countryname"), all.x = TRUE)

wgidataset_origin_2021 <- filter(wgidataset, year == 2021) # Origine en 2021
wgidataset_canada <- filter(wgidataset, countryname == "Canada") #Canada à l'arrivée
wgidataset_canada_2021 <- filter(wgidataset, countryname == "Canada" & year == 2021)

trajipaq <- trajipaq %>%
  left_join(wgidataset_origin_2021, by = c("Q11" = "countryname"))%>%
  left_join(wgidataset_canada, by = c("annee_qc" = "year"))

trajipaq <- trajipaq %>%
  rename_with(~sub("\\.y$", "_2021_origin", .), ends_with(".y"))%>%
  rename_with(~sub("\\.x$", "_arrival_canada", .), ends_with(".x"))
